Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-15 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
更新表格

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[h]
\centering
\resizebox{0.4\textwidth}{!}{%
\begin{tabular}{c|ccc}
\toprule
backbone & googlenet & alexnet & ShuffleNetV2x1.0 \\ \midrule
FGT-AO   & 0.818     & 0.572   & 0.135\\
FGT-SR-50& 0.890     & 0.640   & 0.134\\ \midrule
GT-AO    & 0.035     & 0.196   & 0.554\\
GT-SR-50 & 0.023     & 0.227   & 0.656\\ \midrule
ROI-AO   & 0.760     & 0.720   & 0.766\\  
ROI-SR-50& 0.897     & 0.850   & 0.888\\ \bottomrule
\end{tabular}%
}
\caption{Different backbone}
\end{table}

>>>>

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{cc|ccc}
\toprule
\multicolumn{2}{c|}{Backbone}                                                     & GoogLeNet & AlexNet & ShuffleNet    \\
\midrule
\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Perturbed\\Videos \end{tabular}} & AO (FGT)& 0.818     & 0.572   & 0.135 \\
                                                                            & SR (FGT)& 0.890     & 0.640   & 0.134 \\
\cmidrule{2-5}
                                                                            & AO (GT) & 0.035     & 0.196   & 0.554\\
                                                                            & SR (GT) & 0.023     & 0.227   & 0.656\\
\midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Clean\\Videos \end{tabular}}     & AO (GT) & 0.760     & 0.720   & 0.766         \\
                                                                            & SR (GT) & 0.897     & 0.850   & 0.888         \\
\bottomrule
\end{tabular}
}
\caption{Different backbone}
\end{table}
